Paper 1 Analysis

### 2015-12-04 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Cost share graph improvements.

<<Cost_Share_Plot, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=1.5, fig.cap="Historical cost shares for capital and labor.", eval=FALSE>>=
ggplot(data = gather(CostShares, key=cost_share, value=value, cs_k, cs_l)) + 
  geom_line(mapping = aes(
    x = Year, 
    y = value, 
    group = cost_share, 
    linetype = cost_share,
    color = cost_share,
    size = cost_share)) +
  facet_grid( ~ Country) +
  ylab("Cost Share") +
  scale_y_continuous(limits=c(-0.2, 1.1), breaks=c(0, 0.5, 1)) +
  geom_hline(aes(yintercept = 0.3), colour="gray50", size=0.1) +
  geom_hline(aes(yintercept = 0.7), colour="gray50", size=0.1) +
  xlab("") +
  scale_x_continuous(breaks=c(1960, 1980, 2000)) +
  scale_color_manual(name = "", 
                     labels=c("k", "l"),
                     values=c("black", "black")) +
  scale_linetype_manual(name="", 
                        labels=c("k", "l"),
                        values=c(2,3)) + 
  scale_size_manual(name="", 
                    labels=c("k", "l"),
                    values = c(0.9, 0.9)) +
  xy_theme()
@

>>>>

<<Cost_Share_Plot, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=2.8, fig.cap="Historical cost shares for capital and labor.">>=
gather(CostShares, key=cost_share, value=value, cs_k, cs_l) %>%
  mutate(
    cost_share = relevelFactor(factor(cost_share), c("cs_l", "cs_k"))
  ) %>%
ggplot() + 
  geom_line(mapping = aes(
    x = Year, 
    y = value, 
    group = cost_share, 
    linetype = cost_share,
    color = cost_share,
    size = cost_share)) +
  facet_grid( ~ Country) +
  ylab("Cost Share") +
  scale_y_continuous(limits=c(0.0, 1.0), breaks=c(0, 0.5, 1)) +
  geom_hline(aes(yintercept = 0.3), colour="gray50", size=0.1) +
  geom_hline(aes(yintercept = 0.7), colour="gray50", size=0.1) +
  xlab("") +
  scale_x_continuous(breaks=c(1960, 1980, 2000)) +
  scale_color_manual(name = "", 
                     labels=c("l", "k"),
                     values=c("black", "black")) +
  scale_linetype_manual(name="", 
                        labels=c("l", "k"),
                        values=c(2,3)) + 
  scale_size_manual(name="", 
                    labels=c("l", "k"),
                    values = c(0.9, 0.9)) +
  xy_theme()
@
